%% ============================================================================
%% MASTER CV (compact style) - José Pedro Nolasco Henriques
%%
%% This file is the FULL master content bank (applications/master_cv.md) rendered
%% in the compact LaTeX style ported from the legacy build-cv-usi builder
%% (validated over 44 applications). It is the LaTeX skeleton AND the verbatim
%% content source for tailored CVs.
%%
%% HOW TO BUILD A TAILORED CV (verbatim selection):
%%   1. Copy this file to applications/<company>_<role>/CV_JoseHenriques_<company>_<role>.tex
%%   2. SELECT + REORDER: keep the blocks relevant to the role, delete the rest,
%%      reorder within each section. Content is verbatim-FIRST: skill rows,
%%      projects, education lines, and headers stay character-for-character.
%%      Experience bullets may be LIGHTLY rephrased when it genuinely improves
%%      role fit (tightening, aligning to the posting's terminology), but facts,
%%      metrics, and scope stay exactly the master's - no new claims, no
%%      escalated numbers, no merged achievements. Verbatim stays the default.
%%      The only fully generative content is the About Me paragraph.
%%   3. Keep the \newpage before SKILLS: tailored CVs are exactly 2 pages -
%%      page 1 = About Me / Education / Work Experience / Languages,
%%      page 2 = Skills / Projects / Other Relevant Experience / References.
%%   4. The About Me paragraph must END with the verbatim sentence:
%%      Get to know me better \href{https://tykelar.github.io}{here}!
%%
%% This master compiles to ~4 pages by design (it is the full bank, like the
%% legacy CV_Complete master). Only tailored CVs have the 2-page rule.
%%
%% Compile with lualatex (fontspec + system Carlito font):
%%   cd applications && lualatex -interaction=nonstopmode -output-directory=<company>_<role> <company>_<role>/CV_....tex
%% ============================================================================

\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,left=2.0cm,right=2.0cm,top=1.6cm,bottom=1.7cm]{geometry}
\usepackage{fontspec}
\setmainfont{Carlito}   % metric-compatible Calibri clone; matches the legacy docx look
\usepackage{xcolor}
\definecolor{cvblue}{HTML}{2E74B5}   % Word heading blue (legacy accent)
\definecolor{cvdark}{HTML}{262626}   % near-black for the contact line
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{needspace}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=cvblue,
    linkcolor=cvblue,
    pdftitle={José Pedro Henriques - CV},
    pdfauthor={José Pedro Nolasco Henriques},
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}
\emergencystretch=1em
\linespread{1.04}
\frenchspacing

% Section heading: ALL-CAPS bold blue with a thin full-width rule hugging the text
\titleformat{\section}
  {\color{cvblue}\bfseries\fontsize{11}{13}\selectfont}
  {}{0pt}{\MakeUppercase}
  [\vspace{-10pt}{\color{cvblue!55}\rule{\textwidth}{0.5pt}}]
\titlespacing*{\section}{0pt}{8pt}{0pt}

% One-line work header: \cvjob{Job Title, Company}{Mon YYYY – Mon YYYY}
\newcommand{\cvjob}[2]{\needspace{4\baselineskip}\vspace{3pt}{\bfseries #1 \textbar{} #2\par}\vspace{-2pt}}
% Optional italic context line directly beneath a work header
\newcommand{\cvcontext}[1]{{\itshape\small\hspace{0.3em}#1\par}\vspace{-3pt}}
% One-line education entry: \cvedu{Degree}{Institution}{Mon YYYY – Mon YYYY}
\newcommand{\cvedu}[3]{{\bfseries #1} \textbar{} #2 \textbar{} #3\par}
% Optional italic thesis/final-project line directly beneath an education entry
\newcommand{\cvedusub}[1]{\vspace{-4pt}{\itshape\small\hspace{0.3em}#1\par}}
% Bare blue separator rule (used where a section has no heading, e.g. above About Me)
\newcommand{\cvrule}{\par\vspace{2pt}{\color{cvblue!55}\rule{\textwidth}{0.5pt}}\par}
% Skills row: \cvskill{Category}{item · item · item}
\newcommand{\cvskill}[2]{\par{\bfseries #1:} #2\par}
% Project entry: \cvproject{Title}{Description}
\newcommand{\cvproject}[2]{\needspace{3\baselineskip}\vspace{2pt}{\bfseries #1}\par\vspace{-4pt}#2\par}

% Compact bullet list
\setlist[itemize]{label=\textbullet,leftmargin=1.15em,itemsep=1.5pt,parsep=0pt,topsep=2pt,partopsep=0pt}

\begin{document}

% ============================================================
%   HEADER  (fixed contact line; no headline)
% ============================================================

{\fontsize{20}{24}\selectfont\bfseries\color{cvblue}José Pedro Henriques\par}
\vspace{1pt}
{\bfseries\color{cvdark}Portuguese \textbar{} (+351) 912 678 001 \textbar{} josepedronolasco@gmail.com \textbar{} Portfolio: \href{https://tykelar.github.io/}{tykelar.github.io} \textbar{} LinkedIn: \href{https://www.linkedin.com/in/josepedroh}{josepedroh} \textbar{} GitHub: \href{https://github.com/Tykelar}{Tykelar}\par}

% ============================================================
%   ABOUT ME  (no heading - separator rule only; the only fully
%   generative content in a tailored CV)
% ============================================================

\cvrule

Computer Engineering MSc and Software Quality Engineer who re-engineers delivery infrastructure, improves engineering velocity, and integrates AI into engineering workflows. At a technology company I led a Lean-driven re-engineering of the delivery pipeline, from diagnosing accumulated technical debt through to measurable gains in delivery speed and reliability, formalized in a master's thesis on Lean CI/CD and AI-ready infrastructure. Alongside this I founded and ran a cooperative through its full operational lifecycle, and bring a systems-level perspective spanning applied AI, immersive technologies, and cybersecurity. Get to know me better \href{https://tykelar.github.io}{here}!

% ============================================================
%   EDUCATION  (one bold line each + thesis/final-project sub-line;
%   full project descriptions still live in Projects;
%   Electrotechnical entry OFF by default in tailored CVs)
% ============================================================

\section{Education}

\cvedu{Master's in Computer Engineering}{Polytechnic University of Leiria}{Sep 2024 – Jul 2026}
\cvedusub{Thesis: Lean-Driven QA \& CI/CD Re-Engineering Towards AI-Ready Infrastructures (18/20)}
\cvedu{Bachelor's in Computational Engineering}{University of Aveiro}{Sep 2021 – Jul 2024}
\cvedusub{Final Project: Big Data Analysis \& Representation, NO2 Air Pollution in VR (17/20)}
\cvedu{Electrotechnical Engineering (1 year)}{ESTGA, University of Aveiro}{Sep 2020 – Jul 2021}

% ============================================================
%   WORK EXPERIENCE  (select 5-6 Glartek bullets in tailored CVs;
%   default lead order: AI agent; Lean >50%; 20% sprint; ~30% handover)
% ============================================================

\section{Work Experience}

\cvjob{Software Quality Engineer, Glartek}{Sep 2025 – Jun 2026}
\cvcontext{AI-native, mobile-first, no-code EHSQ (Environment, Health, Safety \& Quality) Connected Worker platform for frontline industrial operations.}
\begin{itemize}
\item Built AI agent skills deployed in internal engineering repositories, enabling automated assistance for complex engineering and process workflows.
\item Led a Lean-driven re-engineering of delivery infrastructure and processes, resolving accumulated technical debt and cutting total pipeline job time by more than 50\%.
\item Redesigned delivery and engineering workflows, contributing to up to 20\% more features deployed per sprint.
\item Restructured task distribution and handovers, reducing time consumption around 30\% and eliminating duplicated work.
\item Contributed to the architecture and testing of an embedded AI chatbot that helps users navigate the platform.
\item Contributed to the architecture and testing of a RAG system letting users query their own uploaded documents.
\item Drove integration of AI agents and services into product and engineering workflows.
\item Collaborated on an in-house image-recognition application built on YOLO object detection: labeled and curated the training dataset, helped define detection classes, and ran and evaluated training and optimization tests.
\item Designed and implemented a test framework in Playwright, including reusable helpers and utilities for scalable coverage.
\item Integrated the automated test battery into GitLab CI pipeline jobs, enabling fully automated execution as part of workflow.
\item Led the Cypress to Playwright migration, including trade-off evaluation, implementation, and documentation.
\item Standardized test naming and data conventions and introduced seed-driven data setup to reduce coupling and instability.
\item Scripted reproducible local and virtual test environments (seed, rebuild, reinitialize services) in Shell/Bash to dev experience.
\item Maintained and extended an existing Cypress battery; analyzed self-built reports and failure patterns to prioritize fixes.
\end{itemize}

\cvjob{Founder \& President, Florescer (Cooperative)}{Jan 2023 – May 2026}
\cvcontext{Non-profit cooperative working on local educational, social, and environmental initiatives.}
\begin{itemize}
\item Founded a non-profit cooperative: legal incorporation, administrative setup, governance structure, and ongoing compliance.
\item Owned the full entrepreneurial process from idea to operational execution with no prior institutional support.
\item Coordinated partnerships with public and private institutions to fund and support community programmes.
\item Led educational activities, community workshops, and public-space renovation initiatives.
\item Organized and monitored internal procedures for consistent operational execution.
\item Managed the full physical setup and operational launch of a café/restaurant space and a nursing-school space.
\end{itemize}

\cvjob{Warehouse Manager Assistant, Airking}{Jul 2020 – Sep 2020}
\begin{itemize}
\item Organized inventory, materials, and warehouse and storage flows.
\item Optimized storage and transport procedures, improving handling and distribution time by up to 20\%.
\item Supported the full logistics cycle (picking, dispatch, transport, retrieval); drove forklift for load handling.
\item Performed technical assembly support, including ventilation conduit assembly.
\end{itemize}

\cvjob{Hospitality Consultant, IMPACT Consulting, Malta}{Jul 2018 – Aug 2018}
\begin{itemize}
\item Built Excel databases from publicly available company information for business outreach.
\item Conducted company and individual outreach for partnership opportunities.
\item Produced documentation linking travel agencies and hospitality brands.
\end{itemize}

% ============================================================
%   LANGUAGES  (one line, closes page 1 in tailored CVs)
% ============================================================

\section{Languages}

Portuguese: Native (C2) · English: C2 · Spanish: B1 · French: A1

% ============================================================
%   PAGE BREAK - tailored CVs keep this so page 2 = Skills onward
% ============================================================
\newpage

% ============================================================
%   SKILLS  (select 6-9 rows per role; keep tool-name rows for ATS)
% ============================================================

\section{Skills}

\cvskill{Process, Operations \& Continuous Improvement}{Process analysis and mapping · Workflow re-engineering · Operational efficiency · Waste identification and prioritization · Procedure standardization · Task ownership and handover design · KPI design and tracking · Lean Software Development · Technical debt diagnosis and remediation · Continuous improvement (PDCA / Kaizen)}
\cvskill{QA, Testing \& Reliability}{Software QA (manual and automated) · End-to-end test framework design (Playwright) · Reusable test helpers and utilities · Cypress maintenance and extension · API integration testing · Component-level unit testing · Test pyramid design and coverage rebalancing · Flaky test mitigation · Seed-driven test data · Failure-pattern and log analysis · Shift-left quality}
\cvskill{CI/CD, DevOps \& Delivery}{CI/CD foundations and practical application · Pipeline optimization and feedback-loop reduction · Build/test resource efficiency · CI job integration for test batteries · Test parallelization · GitLab MR label and workflow governance · Local environment automation scripting · Environment reproducibility · Tooling and migration assessment}
\cvskill{Applied AI \& Machine Learning}{CNNs and image classification · YOLO object detection · RNNs and sequence prediction · Transfer Learning · Hyperparameter optimization (Optuna) · LLM integration and AI agents · RAG system design, testing and evaluation (recall@k benchmarking) · Chatbot and embedded AI chat · Local LLM deployment (Ollama, Gemma) · Prompt engineering}
\cvskill{Cybersecurity \& Defensive Engineering}{Offensive security · OSINT and footprinting · Vulnerability assessment and reporting · SIEM implementation and log centralization · Threat detection and alerting · Host-based intrusion detection (HIDS) · File integrity monitoring · Wazuh and Elastic Stack (ELK)}
\cvskill{Immersive Tech, 3D \& Visualization}{Virtual and Augmented Reality · Digital Twins · 3D modelling and printing · VTK 2D/3D/VR visualization · Unity (C\#) · Godot · Blender · VRChat SDK · Additive manufacturing and rapid prototyping}
\cvskill{Data, Analysis \& Reporting}{Excel database creation and maintenance · Data structuring and reporting · SQL data handling · SPSS statistics · KPI and operational metric tracking · Analytical reasoning}
\cvskill{Engineering Foundations}{Physics and Mathematics (classical and quantum mechanics) · Scientific computing and simulation (MATLAB) · Engineering drawings · Systems and computer hardware architecture · Elementary electrical circuits}
\cvskill{Programming Languages}{Python · TypeScript · JavaScript · Java · C\# (Unity) · React Native · SQL Server / SQL · MATLAB · Shell / Bash · Assembly · C}
\cvskill{Tools \& Platforms}{Playwright · Cypress · GitLab CI · Bash / Shell · Git · MS Project · Excel · SQL · SPSS · Unity · Godot · Blender · VRChat SDK · VTK · Ollama (Gemma) · Wazuh · Elastic Stack (ELK) · Microsoft 365}
\cvskill{Soft Skills}{Initiative and autonomy · Problem-solving (root-cause-first) · Fast learning and resilience · Leadership and team dynamics · Communication with technical and non-technical stakeholders · Adaptability}

% ============================================================
%   PROJECTS  (always include; thesis entry first by default;
%   select 3-5 per role in tailored CVs)
% ============================================================

\section{Projects}

\cvproject{Lean-Driven QA \& CI/CD Re-Engineering Towards AI-Ready Infrastructures (Master's Thesis)}{Research into engineering infrastructures that stay scalable, understandable, and ready for AI integration: CI/CD architecture, QA integration, shift-left quality, flakiness dynamics, and toolchain-migration criteria. Directly informed by the Glartek work.}

\cvproject{Big Data Analysis \& Representation: NO2 Air Pollution in VR (Bachelor's Final Project)}{A VR system for visualizing large-scale NO2 air-pollution data across an urban area, built with OpenXR, VTK, and Unity, with a user study comparing VR and desktop interaction. Supervised by Prof. Paulo Dias (IEETA, University of Aveiro).}

\cvproject{Niche-Field SaaS Marketing \& Admin Platform}{A full-stack, multi-tenant SaaS web platform delivered solo end to end in a pnpm monorepo: React + Vite frontend and an Express REST API deployed as serverless functions on Vercel, sharing one Zod-derived, end-to-end type-safe API contract; PostgreSQL via Drizzle ORM with schema-first validation; stateless JWT auth chosen specifically for the serverless backend; server-side Mapbox geocoding and Cloudflare R2 file storage via presigned uploads; Upstash-backed rate limiting; and a Playwright e2e test suite.}

\cvproject{Shared Expense Tracker (Serverless PWA)}{A private, installable expense-tracking PWA for two people, delivered solo end to end with no backend of my own to run: React, Vite, and Supabase (managed Postgres, Auth, Realtime), authorization enforced entirely through Postgres Row-Level Security, a hand-rolled \textasciitilde60-line reactive data layer replacing Redux/Zustand, Google OAuth sign-in, and Workbox-based offline/installable support, deployed as static hosting only.}

\cvproject{Minimal Local RAG System (Python + Ollama)}{A from-scratch, fully local retrieval-augmented-generation pipeline indexing personal project documentation and answering questions entirely offline (Python, Ollama, nomic-embed-text, Gemma). Built a recall@k evaluation harness against a golden question set, then identified and corrected an overly permissive evaluation methodology, turning the retrieval-depth (k) choice from an assumption into an empirically justified decision.}

\cvproject{SIEM Implementation: Security Monitoring \& Detection}{Designed and deployed a working SIEM (Wazuh + Elastic Stack) centralizing log collection, with detection rules, alerting, file integrity monitoring, and host-based intrusion detection, validated against simulated attacks.}

\cvproject{Cybersecurity Assessment \& Footprinting (Client Project)}{External attack-surface mapping through footprinting and OSINT for a small cooperative; delivered a prioritized vulnerability and remediation report and presented it to the client.}

\cvproject{Digital Twin \& Animal Tracking App}{A mobile system keeping a live digital twin of tracked animals across large-scale environments, with two-way communication and an AR layer mapping positions in real space. Built with Kotlin, React Native, Firebase, and A-Frame.}

\cvproject{1:1 Architectural VR Walkthrough (Client Project)}{Accurate 1:1-scale 3D building models navigable on desktop and in VR (Unity), used by clients to plan interior decoration in a spatially accurate representation of their space.}

\cvproject{Mobile Client-Management App (Cooperative)}{A React Native + Firebase app letting a cooperative access and manage client information on the go, delivered end to end.}

\cvproject{Sign Language Recognition: Image-to-Text (Academic)}{A computer-vision system reading sign-language gestures from images and converting them to text at 98\% classification accuracy (Python).}

\cvproject{CNN Match Classification: League of Legends (Academic)}{A multiclass-multilabel CNN over spatial heatmap images predicting match outcome, player role, and duration; compared single-input, per-output, Transfer Learning, and Optuna-optimized architectures.}

\cvproject{Further Academic ML \& Computing}{YOLO multi-class object detection at scale; RNN sequence prediction; MATLAB physics and mathematics simulations; SPSS statistical analysis across research cases.}

\cvproject{Game Design \& Development and Maker Practice}{Independent multi-engine game development (Unity, Godot, Blender, VRChat SDK) with published content, plus an ongoing home 3D modelling and printing practice for rapid prototyping.}

% ============================================================
%   OTHER RELEVANT EXPERIENCE  (select 2-4 in tailored CVs)
% ============================================================

\section{Other Relevant Experience}

\begin{itemize}
\item International exposure: travel across 16+ countries, training courses in Finland, Poland, and Portugal, and six months living in Poland (Erasmus+).
\item Founded a student-run radio station using governmental funds for school-improvement, sourced, and set up the equipment.
\item 18+ years of Scouting across national and international activities, including World Scout Jamboree participation.
\item Scout experience for 18+ years; volunteer work across forest conservation, food distribution, and animal welfare; community ambassador roles (Unlimited Future, Quinta da Carvalheira).
\item Personal maker practice: home-based 3D modelling and printing for rapid prototyping and iterative problem-solving.
\item Writing: two personal blogs on personal growth/psychology and creative writing.
\end{itemize}

% ============================================================
%   REFERENCES  (single line; never print referee contact details)
% ============================================================

\needspace{4\baselineskip}
\section{References}

Formal recommendation letter from the CTO of Glartek, available on request; additional references on request.

\end{document}
